%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
  {Open-Source Contributor} % Job title
  {Incompact3D} % Organization
  {GitHub} % Location
  {Jul. 2024 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed a fortran subroutine to calculate lift and drag forces for a 3D immersed body simulations using Incompact3D.}
      \item {Working on improving the performance of importing STL files for high-fidelity simulations using Incompact3D.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Research Intern} % Job title
  {Indian Institute of Technology, Kharagpur} % Organization
  {Kharagpur, India} % Location
  {Mar. 2022 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Investigating the aerodynamics of birds through computational methods with implementation in aircraft design under the guidance of Dr. Sandeep Saha, IIT KGP and Dr. Manu KV, IIST.}
      \item {Conducted high-fidelity direct numerical simulations on Paramshakti and Virgo clusters of IIT KGP and IIST respectively using Incompact3D and NEK5000.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Chief Coordinator} % Job title
  {Conscientia, IIST} % Organization
  {Thiruvananthapuram, India} % Location
  {Mar. 2023 - Nov. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Organized and managed the 14th edition of IIST's technical and astronomical festival, Conscientia, from September 22nd to 25th, 2023.}
      \item {Conducted competitions and workshops, attracting over 1,000 student participants from across India.}
      \item {Oversaw a budget of approximately 22 lakhs, generating a profit of 4 lakhs.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Website Coordinator} % Job title
  {Conscientia, IIST} % Organization
  {Thiruvananthapuram, India} % Location
  {Aug. 2022 - Nov. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and managed the website of 13th edition of IIST's technical and astronomical festival, Conscientia 2023.}
      \item {Designed the front-end of the website using Vanilla and Django.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Student Member \& Student Coordinator} % Job title
  {AeroClub, IIST} % Organization
  {Thiruvananthapuram, India} % Location
  {Mar. 2022 - Nov. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and built fixed-wing and rotor-based model aircrafts.}
      \item {Conducted workshops on "UAV Design" for school students with a pratical glider building session.}
      \item {Conducted sessions for junior members of the club on UAV Design including glider and water-rocket design competitions.}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
