%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Honors \& Awards}


%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{International Awards}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
  {4th Place} % Award
  {Scientist of the Future 2020, Moscow State University} % Event
  {Online} % Location
  {2020} % Year
  {
    \begin{cvitems}
      \item Represented India in the competition in the Physics and Astronomy category.
      \item Our work titled \emph{Formation and sticking of air bubbles in water in d-block containers} was awarded 4th position. 
      \item Later, the work was published in the Journal of Emerging Investigators.  
    \end{cvitems}
  }

  \cventry
  {Team India} % Award
  {Beamline for School, CERN} % Event
  {Online} % Location
  {2021} % Year
  {
    \begin{cvitems}
      \item Represented India in the competition and proposed a physics problem to be performed on the Beamline setup.
      \item Our group had proposed an idea to study the physics of semi-conductors with electron and positron.
    \end{cvitems}
  }
\end{cventries}

%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\vspace{0.5cm}
\cvsubsection{Domestic Awards}

\begin{cventries}
  %---------------------------------------------------------
  \cventry
  {Finalist} % Award
  {Young Scientist India} % Event
  {Chennai, India} % Location
  {2021} % Year
  {
    \begin{cvitems}
      \item Presented a concept of a wearable device based on flex sensor as accessibility aid for differently abled people.
      \item The idea was selected as a finalist in the competition. 
    \end{cvitems}
  }
  
  %---------------------------------------------------------
  \cventry
  {Certificate of Merit (AISSCE)} % Award
  {Central Board of Secondary Education} % Event
  {Delhi, India} % Location
  {2021} % Year
  {
    \begin{cvitems}
      \item Awarded in grade XII for outstanding performance in the AISSCE examination with 100\% score in English.  
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Certificate of Merit (AISSE)} % Award
  {Central Board of Secondary Education} % Event
  {Delhi, India} % Location
  {2019} % Year
  {
    \begin{cvitems}
      \item Awarded in grade X for outstanding performance in the AISSE examination with 100\% score in Science, Social Science and Mathematics.  
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Certificate of Merit} % Award
  {Government of West Bengal} % Event
  {Kolkata, India} % Location
  {2019} % Year
  {
    \begin{cvitems}
      \item Awarded by honorable Chief Minister, Government of West Bengal for outstanding performance in AISSE board.
      \item Achieved 4th position in state of West Bengal.  
    \end{cvitems}
  }
\end{cventries}

%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
% \cvsubsection{Community}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
% \begin{cvhonors}

% %---------------------------------------------------------
% \end{cvhonors}
