%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open-Source Contributions}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
  {High-order finite difference flow solver} % Job title
  {Incompact3D} % Organization
  {CFD, Fortran} % Location
  {GitHub} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed a fortran subroutine to calculate lift and drag forces for a 3D immersed body simulations using Incompact3D.}
      \item {Working on improving the performance of importing STL files for high-fidelity simulations using Incompact3D.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {A Python software suite for NEK5000 and SIMSON} % Job title
  {PyMech} % Organization
  {CFD, Python, NEK5000} % Location
  {GitHub} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Improving the in-built open\_dataset function to support unstructured datasets produced using NEK5000.}
      \item {Used for post-processing of high-fidelity simulation data using NEK5000.}
    \end{cvitems}
  }
  %---------------------------------------------------------

  %---------------------------------------------------------
  \cventry
  {A course in Turbulence simulation} % Job title
  {TurbCourse} % Organization
  {CFD, Python, NEK5000} % Location
  {GitHub} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Improved the performance of POD and DMD modules for high-fidelity simulation data using NEK5000.}
      \item {Added capability for conducting frequency analysis of the POD modes.}
      \item {Uses PyMech for reading/writing of NEK5000 data.}
    \end{cvitems}
  }
  %---------------------------------------------------------

  %---------------------------------------------------------
  \cventry
  {A Beamer template for IIST students} % Job title
  {IIST-Beamer-Template} % Organization
  {LaTeX, Beamer} % Location
  {GitHub, Overleaf} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created a minimal and simple beamer template for IIST students.}
      \item {It provides a structured and visually appealing way to create presentations that meet academic and professional standards.}
    \end{cvitems}
  }
  %---------------------------------------------------------
\end{cventries}
