%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  %---------------------------------------------------------
  \cventry
  {Research Internship} % Course if relevant
  {Aerodynamics of Avian Tails} % Title
  {CFD, Fortran, Python} % Skills
  {Mar 2023 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s)
      \item {High-fidelity simulations were conducted to understand the role of avian tail in gliding flight.}
      \item {The Common Swift was modelled and 2D-DNS simulations were conducted using NEK5000.}
      \item {RANS-assisted 3D DNS were conducted using SU2 and NEK5000.}
    \end{cvitems}
  }
  %---------------------------------------------------------
  \cventry
  {AE412: Aerospace Vehicle Design} % Course if relevant
  {Design and development of a Loitering Munition} % Title
  {Aircraft Design, Python} % Skills
  {Aug 2024 - Nov 2024} % Date(s)
  {
    \begin{cvitems} % Description(s)
      \item {A low-cost loitering munition with a payload capacity of 2 KG is being designed and developed.}
      \item {Undertaken conceptual and preliminary design of the loitering munition.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {IIT Kharagpur} % Course if relevant
  {Development of 3D Force calculation subroutine for Incompact3D} % Title
  {CFD, Fortran, HPC} % Skills
  {May 2024} % Date(s)
  {
    \begin{cvitems} % Description(s)
      \item {A fortran subroutine was developed to enable 3D forces calculation in Incompact3D, a finite difference solver for N-S equations.}
      \item {The subroutine was developed and merged with the original code as an open-source contribution on GitHub.}
      \item {Open-source and available on GitHub.}
    \end{cvitems}
  }
  % %---------------------------------------------------------

  \cventry
  {IIT Kharagpur} % Course if relevant
  {FreeFEM-Euler} % Title
  {CFD, FreeFEM++, GMSH} % Skills
  {Jun. 2024} % Date(s)
  {
    \begin{cvitems} % Description(s)
      \item {An incompressible flow solver based on Artificial Compressibility Method was developed using FreeFEM++.}
      \item {The code is capable of solving 2D and 3D problems based on in-built FreeFEM++ and GMSH meshes.}
      \item {Open-source and available on GitHub.}
    \end{cvitems}
  }
  
  % %---------------------------------------------------------
  \cventry
  {SSPACE Labs} % Course if relevant
  {UHF/VHF Standalone Antenna Mast Retraction Mechanism} % Title
  {Mechanisms, CAD} % Skills
  {Dec. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s)
      \item {The institute's SSPACE Labs have been using an UHF/VHF Standalone antenna for establishing communication with the INSPIRESAT-1 satellite.}
      \item {A retraction mechanism for the antenna was designed such that it can be retracted easily for maintainence purposes.}
    \end{cvitems}
  }

  % %---------------------------------------------------------
  \cventry
  {AE111: Introduction to Aerospace Engineering} % Course if relevant
  {Performance Analysis of Boeing C17 Globemaster} % Title
  {Aircraft Performance} % Skills
  {Feb. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s)
      \item {The performance of C17 Globemaster was analyzed in this project.}
      \item {The various performance parameters presented by the manufacturer and experimentally tested by operators were analysed using theoretical analysis.}
    \end{cvitems}
  }

  % %---------------------------------------------------------
  \cventry
  {AE131: Basic Engineering Lab} % Course if relevant
  {Thrust Vectoring Nozzles of Sukhoi Su30-MKI} % Title
  {Mechanisms, CAD} % Skills
  {Feb. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s)
      \item {The mechanism of the Thrust Vectoring Nozzles of Sukhoi Su-30 MKI was studied under this project as mechanical report.}
      \item { A CAD model of the mechanism was also made in Fusion 360 and it was simulated.}
    \end{cvitems}
  }
\end{cventries}
